Transfer report

### 2018-08-08 Report/paper-data.Rmd
Adds paper data rmd

```{r setup, include=FALSE}
library(ggplot2)
library(ez)
library(dplyr)
library(reshape2)
library(broom)
library(brainvr.R)
library(restimoter)
source("../Scripts/loading.R")
source_folder("../TwoWorlds")
source('../Scripts/analysis-helpers.R')
sop_all <- read.table("../sop.csv", sep=";", header = T, stringsAsFactors = F)
walk_all <- read.table("../walk.csv", sep=";", header = T, stringsAsFactors = F)
walk_all$learning.condition <- walk_all$condition
walk_all$learning.condition <- recode(walk_all$learning.condition, "real-real" = "Real", "ve-real" = "Desktop", "vr-real" = "Treadmill VR", "real-vr" = "Real", "vr-vr" = "Treadmill VR")
sop_all$learning.condition <- sop_all$condition
sop_all$testing.condition <- sop_all$condition
sop_all$learning.condition <- recode(sop_all$learning.condition, "real-real" = "Real", "ve-real" = "Desktop", "vr-real" = "Treadmill VR", "real-vr" = "Real", "vr-vr" = "Treadmill VR")
sop_all$testing.condition <- recode(sop_all$testing.condition, "real-real" = "Real", "ve-real" = "Real", "vr-real" = "Real", "real-vr" = "Treadmill VR", "vr-vr" = "Treadmill VR")

>>>>

```{r setup, include=FALSE}
library(ggplot2)
library(ez)
library(dplyr)
library(reshape2)
library(broom)
library(brainvr.R)
library(restimoter)

source("../Scripts/loading.R")
source_folder("../TwoWorlds")
source('../Scripts/analysis-helpers.R')
sop_all <- read.table("../sop.csv", sep=";", header = T, stringsAsFactors = F)
walk_all <- read.table("../walk.csv", sep=";", header = T, stringsAsFactors = F)
walk_all$learning.condition <- walk_all$condition
walk_all$learning.condition <- recode(walk_all$learning.condition, "real-real" = "Real", "ve-real" = "Desktop", "vr-real" = "Treadmill VR", "real-vr" = "Real", "vr-vr" = "Treadmill VR")
sop_all$learning.condition <- sop_all$condition
sop_all$testing.condition <- sop_all$condition
sop_all$learning.condition <- recode(sop_all$learning.condition, "real-real" = "Real", "ve-real" = "Desktop", "vr-real" = "Treadmill VR", "real-vr" = "Real", "vr-vr" = "Treadmill VR")
sop_all$testing.condition <- recode(sop_all$testing.condition, "real-real" = "Real", "ve-real" = "Real", "vr-real" = "Real", "real-vr" = "Treadmill VR", "vr-vr" = "Treadmill VR")
